---
title: "Replication of Asutay & Västfjäll, 2017, Experiment 1"
output:
  html_document:
    df_print: paged
---
```{r include=FALSE}
  library(tidyverse)
  library(ez)
  load("../data/ratings.Rdata")
  load("../data/searches.Rdata")
```
We first load our prepared data files.

- ratings.Rdata (valence ratings) & searches.Rdata (response times for VO and VA)
- these files are filtered for accuracy on the participant level, ie, participants who might have switched response keys are not included: [1]  14  42  60  65 100
- this leaves us with
```{r}
  length(unique(searches$respondent))
```
participants.

# Accuracy

We calcualate per condition (sound / visual) average reaction time and % accuracy to replicate Table 1.
```{r}
    searches %>%
      group_by(salience, sound) %>%
      summarise(RT = mean(responseTime),
                Accuracy = sum(accuracy)/length(accuracy))
```

Overall there are `r round(sum(searches$accuracy)/length(searches$accuracy)*100,1)`% of trials correct. We remove the inccorect ones for the following calculations.

# Valence distribution on an individual base for the fours sounds. Reproducing Figure 2B.

- remove incorrect trials - searches.acc
- rank order stimuli based on arousal level into S1 to S4 per individual
- count valence ratings and make (somewhat ugly) stacked barplot

```{r}
# remove incorrect trials
  searches.acc <- 
    searches %>%
    filter(accuracy == 1)
 
 # order stimuli based on arousal level into S1 to S4
  arousal.level <- 
  ratings %>%
    filter(event == 'arousal_rating') %>%
    group_by(respondent) %>%
    arrange(desc(value), .by_group = TRUE)
  # add S1 - S4    
  arousal.level$arousal <- rep(c('S1', 'S2', 'S3', 'S4'), length(unique(arousal.level$respondent)))
  
# plot rating across audiory stimuli
  arousal.level.count <- 
  arousal.level %>%
    group_by(arousal, stim_id) %>%
    summarise(count_stim = n())

  ggplot(arousal.level.count, aes(x = arousal, y = count_stim, fill = stim_id)) +
    geom_bar(stat = 'identity') + 
    ylab('Number of Subjects') + 
    xlab(NULL) + 
    scale_fill_grey() + 
    theme_minimal(base_family = 'mono', base_size = 18) + 
    theme(legend.title=element_blank())
```


# Reaction times for high v. low salient targets. Reproducing Figure 2B.

- split into searches.VA and searches.VO (add variable arousal)
- put together again and order factor levels

```{r}
  # select relevant variables
  arousal.level.short <- 
  arousal.level %>%
    select(respondent, stim_id, arousal)
  
  # searches VA
  searches.VA <- 
    searches.acc %>%
    filter(block == 'VA')
  
  # searches VO
  searches.VO <- 
    searches.acc %>%
    filter(block == 'VO') %>%
    mutate(arousal = 'V') #visual only
  
  # merge into searches file
  searches.VA <-  merge(searches.VA, arousal.level.short, by.x = c('respondent', 'sound'), by.y = c('respondent', 'stim_id'))
  # put back together
  searches.arousal <- rbind(searches.VA, searches.VO)
  

```

This gives us the following figure (2A):

```{r}

# reorder factor to represent Figure 2 order of Asutay et al., 2017
  searches.arousal$arousal <- as.factor(searches.arousal$arousal)
  searches.arousal$arousal <- factor(searches.arousal$arousal, levels = c("V", "S1", "S2", "S3", "S4"))
  
  ggplot(searches.arousal, aes(arousal, responseTime, colour = salience)) +
    stat_summary(fun.y = mean, geom = "point", size = 2) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) + 
    facet_grid(salience ~ ., scales = "free") +
    theme_minimal(base_family = 'mono', base_size = 18) +
    ylab('RT [ms]') + 
    xlab('Stimulus') +
    theme(legend.position="none")
```

# Stats for main hypotheses

- we reproduce a significant main effect of salience and position; as well as 
```{r}
# convert to factors
  searches.VO$respondent <- as.factor(searches.VO$respondent)
  searches.VO$position <- as.factor(searches.VO$position)
  searches.VO$salience <- as.factor(searches.VO$salience)

# Does arousal induced by task-irrelevant auditory stimuli modulate attention in a visual search?
  searches.long <-
  searches.arousal %>%
    filter(block == 'VO') %>%
    filter(!is.na(responseTime)) %>%
    select(respondent, trial_nr, salience, position, responseTime)
  
# run anova with the excellent ez package (loaded above)
  ezANOVA(data = searches.VO,
          dv = responseTime,
          wid = respondent,
          within = .(salience, position),
          type = 3)
  # and show some means
  searches.VO %>%
    group_by(salience) %>%
    summarise(av_sal = mean(responseTime),
              sd_sal = sd(responseTime))
  
  searches.VO %>%
    group_by(position) %>%
    summarise(av_pos = mean(responseTime),
              sd_pos = sd(responseTime))
```

- add the interaction of salience and position in VO

```{r}
  ggplot(searches.VO, aes(salience, responseTime, group = position, colour = position )) +
  stat_summary(fun.y = mean, geom = "point") +
    stat_summary(fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) + 
    theme_minimal(base_family = 'mono', base_size = 18) 
```

```{r}
  # switch to mixed model approach  
  library(lme4)
  #install.packages('lmerTest', repos = c('http://rforge.net', 'http://cran.rstudio.org'))
  library(lmerTest)
    my_lmer = lmer(responseTime ~ (1|respondent) + arousal * position * salience, data = searches.VA)
    summary(my_lmer)
```

